The Nature and Orbit of the Ophiuchus Stream

### 2014-12-29 tex/ms.tex
Implement Jo\'s comments on Section \'Time of disruption\'

To create a more realistic stream that includes a progenitor, we use the
gyrfalcON code \citep{deh00,deh02} in the NEMO toolkit \citep{teu95}. We set up
the progenitor as a King cluster \citep{kin66} with a mass of $1\times10^4$
$M_\sun$, tidal radius of 94 pc and a ratio of the central potential to the
velocity dispersion squared of 2.0 (i.e., a concentration parameter of 2). The
cluster is sampled using 20,000 particles and is evolved for $\sim375$ Myr in
the MWPotential2014 potential. The initial conditions are those at the
$t\sim-375$ Myr apocenter of the most probable orbit of the Ophiuchus stream.

@@

If the Ophiuchus stream is all that is left of the progenitor, and if the
progenitor was disrupted 250 Myr ago as our simulations suggest, how did the
progenitor remain bound for 13 Gyr (which is the age of the stream's
population) on this fairly short orbit? If the progenitor was on this orbit for
the past 13 Gyr, it would have passed through the disk more than 40 times.
What was so special about the disk passage 250 Myr ago, compared to all the
previous disk passages? On the other hand, if the progenitor was not always on
this orbit, and if its apocentar was more distant (like that of Pal 3), how did
its orbit change? Even though we believe we have resolved a few mysteries
related to the Ophiuchus stream, more mysteries remain.

>>>>

To create a more realistic stream that includes a progenitor, we use the
gyrfalcON code \citep{deh00,deh02} in the NEMO toolkit \citep{teu95}. We set up
the progenitor as a King cluster \citep{kin66} with a mass of $1\times10^4$
$M_\sun$, tidal radius of 94 pc and a ratio of the central potential to the
velocity dispersion squared of 2.0. The cluster is sampled using 20,000
particles and is evolved for $\sim375$ Myr in the MWPotential2014 potential. The
initial conditions are those at the $t\sim-375$ Myr apocenter of the most
probable orbit of the Ophiuchus stream.

@@

If the Ophiuchus stream is all that is left of the progenitor, and if the
progenitor was disrupted 250 Myr ago as our simulations suggest, how did the
progenitor remain bound for 13 Gyr (which is the age of the stream's
population) on this fairly short-period orbit? If the progenitor was on this
orbit for the past 13 Gyr, it would have passed through the disk more than 40
times. What was so special about the disk passage 250 Myr ago, compared to all
the previous disk passages? On the other hand, if the progenitor was not always 
on this orbit, and if its apocentar was more distant (like that of Pal 3), how
did its orbit change? Even though we believe we have resolved a few mysteries
related to the Ophiuchus stream, more mysteries remain.
